Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-08 R0V0.tex
Start to change the example to take into account the changes on the set \Xi

When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
N^2\begin{pmatrix}
n+d\\ d
\end{pmatrix}^2
\end{equation*}
equations to be solved. This motivates the approach proposed in this paper.

@@

In all cases, the matrix $W$ was required to have a block-diagonal structure as follows
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),
\end{equation*}
the definition of the matrices $W_a$ and $W_b$ differs, according to each case considered.

In the first one, no constraints were imposed on the matrix $Y$ (it was defined as a full matrix). More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and for each $i$ $\mathbf{X}(\mathscr{K}(k))=\{x\}$. The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}. The components of the matrix $W$ and the matrix $Y$ that form a solution to \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\\
 \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
\end{align*}

@@

For the remaining cases, the constraints imposed on the matrix $Y$ are such that the matrix of the left-hand-side of the MI \eqref{eq:MI formulation} is given by
\begin{equation*}
	\mathbin{\mathtt{diag}}\left(\begin{bmatrix}
		T_{11}&T_{12}\\
		T_{12}^\top&T_{22}
	\end{bmatrix},\cdots,\begin{bmatrix}
		T_{(N-1)(N-1)}&T_{(N-1)N}\\
		T_{(N-1)N}^\top&T_{NN}
	\end{bmatrix}\right).
\end{equation*}
This implies that sparsity can be exploited to decrease the number of equations needed to verify the MI \eqref{eq:MI formulation}.

In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$. Consequently, for each index $i\in\mathbb{N}_{[1,4]}$, the non-identically zero elements of the $i$-th line of the matrix $Y$ depend on the variables $q_{i-1}$, $q_i$ and $q_{i+1}$ (note that, for convenience, $q_0:=q_1$ and $q_5:=q_4$).

>>>>

When $N\geq6$ and $Y$ is a full matrix with elements described by polynomials, the MI \eqref{eq:MI formulation} could not be solved with the optimization parser Yalmip \cite{Loefberg2004,Loefberg2009} and the solver Mosek running on an Intel Core i7, 8GB RAM, Microsoft Windows 10 and on Matlab 2015b. A reason for this issue is the dependence of each element of the matrix $Y$ on the variable $q$. Another reason is the need to verify if the matrix \eqref{eq:MI formulation} is negative definite. For instance, when  polynomials with degree $d$ are employed, the number of monomials to be optimized in the $(i,j)$ position the matrix $T$ is
\begin{equation*}
		\begin{pmatrix}
n+d\\ d
\end{pmatrix}
\end{equation*}
\cite{Waki2006}. Consequently, when no structural constraints are imposed on $Y$, this verification can lead to
\begin{equation*}
N\dfrac{N+1}{2}\begin{pmatrix}
n+d\\ d
\end{pmatrix}^2
\end{equation*}
equations to be solved. This motivates the approach proposed in this paper.

@@

In all cases, the computed matrix $W$ has a block-diagonal structure as follows
\begin{equation*}
 W=\mathbin{\mathtt{diag}}\left(W_a,W_b,W_b,W_a\right),
\end{equation*}
the definition of the matrices $W_a$ and $W_b$ differs, according to each case considered.

In the first one, no constraints were imposed on the matrix $Y$ (it is defined as a full matrix). More precisely, for each $k\in\mathbb{N}_{[1,4]}$, $\mathscr{K}(k)=\{1,2,3,4\}$, for each $j\in\mathbb{N}_{[1,8]}$, $\mathbf{C}_j=\mathbb{R}^8$, and $\mathbf{X}(\mathscr{K}(k))=\{x\}$, for each $k\in\mathbb{N}_{[1,4]}$. The parser took 98  seconds to solve the MI \eqref{eq:MI formulation}. The components of the matrix $W$ and the matrix $Y$ that form a solution to \eqref{eq:MI formulation} are
\begin{equation*}
		W_a=\mathbin{\mathtt{diag}}\left(
 1.27,1.53\right),\quad W_b=\mathbin{\mathtt{diag}}\left(1.08,1.53\right)
\end{equation*}
and the matrix $Y$ has the structure shown in Equation~\eqref{eq:example:Y:general} with elements
\begin{align*}
 \overline{Y}_{ij}(q)=&-3y_i-0.08x_iy_i\\
 \underline{Y}_{ij}(q)=&-2+0.009x_i-1.2\sum_{k=1}^4 y_k^2+x_k^2.
\end{align*}

@@

For the remaining cases, the structure of the network composed of systems of the form \eqref{eq:example}. More specifically, Proposition~\ref{prop:clique tree decomposition} can be employed, as the graph describing the interconnection of the network is a subclass of chordal graphs.

The constraints imposed on the matrix $Y$ are such that the matrix of the left-hand-side of the MI \eqref{eq:MI formulation} is given by
\begin{equation*}
	\mathbin{\mathtt{diag}}\left(\begin{bmatrix}
		T_{11}&T_{12}\\
		T_{12}^\top&T_{22}
	\end{bmatrix},\cdots,\begin{bmatrix}
		T_{(N-1)(N-1)}&T_{(N-1)N}\\
		T_{(N-1)N}^\top&T_{NN}
	\end{bmatrix}\right).
\end{equation*}

In the ``neighbor'' case, the constraint imposed on the matrix $Y$ was that each line of this matrix should depend on the system $i$ and on its neighbors. The the set $\mathscr{K}$ is defined, for each index $i=2,3$, as $\mathscr{K}(i)=\{i-1,i,i+1\}$, $\mathscr{K}(1)=\{1,2\}$ and $\mathscr{K}(4)=\{3,4\}$.

\todo[inline]{From here}

For each $j\in\mathbb{N}$, $\mathbf{C}_j$

Consequently, for each index $i\in\mathbb{N}_{[1,4]}$, the non-identically zero elements of the $i$-th line of the matrix $Y$ depend on the variables $q_{i-1}$, $q_i$ and $q_{i+1}$ (note that, for convenience, $q_0:=q_1$ and $q_5:=q_4$).
